\papertitle

### 2014-03-18 final-report/paper.tex
Bug

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overview\xspace}

@@

\title{\papertitle}
\numberofauthors{1}
\author{\alignauthor Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres \\
\affaddr{Dept. of Computer Science, University of Washington} \\ \affaddr{Seattle, Washington, USA} \\
\email{\texttt{\{ujaved, moreau, domoritz, aaasz\}@cs.washington.edu}}
}

@@

% What is myria, how does it work (look at report from last quarter but shorter), which query languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions
% so far the only performance debug mechanism is runtime
% contributions
% explain difference between execution and data skew

\todo{write me}

\begin{itemize}
    \item problem: hard to learn why a query is slow
    \item motivation: help developers/programmers dig what the problems might be
    \item Questions: find data/execution skew, identify performance bottlenecks, visualize data flow in the system (elaborate on each point)...
\end{itemize}

@@

The Myria web front-end server is written in Python and runs on Google App Engine\footnote{\url{https://developers.google.com/appengine/}}. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.

@@

% Figures
% 1: Graph with back-edge
% 2: Large Graph expanded vs. large Graph reduced vs. large graph expanded -1

@@

\textbf{Graph Rendering:} We use D3 \cite{d3} to render the \graph graph, which allows us to support various interactions and transistions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations.

@@

\textbf{Tooltip Information:} \todo{write me}

\subsubsection{Fragment execution view}
\label{sec:fragment}

@@

% Dom

The \overall shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.

@@

\todo{write me}

@@

We used \system to examine real world database queries that ran on Myria. We base our analysis on the different visualizations that were generated by \system and present examples where the \system helped us better identify (1) data skew, (2) execution skew, (3) performance bottlenecks.

We explore a simple join query we performed on one million tuples extracted from the Twitter user graph. This query joins Twitter followers and followees by user ID. The query can be written in SQL as expressed below.

\begin{lstlisting}
SELECT *
FROM twitter S, twitter R
WHERE S.follower = R.followee
\end{lstlisting}

The resulting \graph visualization is displayed in Figure~\ref{fig:TODO}. The user will navigate the \graph visualization in the browser panel in the next case studies to identify several performance symptoms.

@@

\subsection{Case 1: Identifying Performance Bottlenecks using the \overall}

%dom

\todo{write me}

\subsection{Case 1: Identifying Data Skew using the \network View}

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}

\usepackage{caption}
% Bug in my version of the caption package
\DeclareCaptionType{copyrightbox}
\usepackage{subcaption}

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

\title{\papertitle}
\numberofauthors{1}
\author{\alignauthor Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres \\
\affaddr{Dept. of Computer Science, University of Washington} \\ \affaddr{ Seattle, Washington, USA} \\
\email{\texttt{\{ujaved, moreau, domoritz, aaasz\}@cs.washington.edu}}
}

@@

% What is myria, how does it work (look at report from last quarter but shorter), which query languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions
% so far the only performance debug mechanism is runtime
% contributions

\begin{itemize}
    \item problem: hard to learn why a query is slow
    \item motivation: help developers/programmers dig what the problems might be
\end{itemize}

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.

@@

@@

\textbf{Graph Rendering:} We use D3 to render the \graph graph, which allows us to support various interactions and transistions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations.

@@

\textbf{Tooltip Information:} TODO

\subsubsection{Fragment execution view}

@@

@@

@@

In this section we will evaluate the different visualizations and elaborate on actual examples where the visualization helped us to find data or execution skew.

@@

\subsection{Network visualization}
